---
title: "Curiosity Project: Student Pilot Data Analysis"
format: 
  html:
        toc: true
        number-sections: true
  pdf:
        toc: true
        number-sections: true
        keep-tex: true
        include-in-header:
                text: |
                  \usepackage{fvextra}
                  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
        include-before-body: 
                text: |
                  \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
                  showspaces = false,
                  showtabs = false,
                  breaksymbolleft={},
                  breaklines
                  }
execute: 
  echo: false
  output: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup

source(here::here("scripts", "01_setup.R"))

```

The raw data from the student pilot test contained 105 responses. 22 of the responses were removed because they were missing names and student ID numbers. An additional 3 responses were removed because they were either `Mike` or nonsensical responses to the question asking for student names (`Q30_1`) or student IDs (`Q30_2`). The final sample size is 80 respondents.

# Experimental Conditions

```{r}
#| label: exp-cond

source(here::here("scripts", "02_exp-cond.R"))

```

The random assignment to conditions appears to have worked fine. The number of respondents per condition ranged from 18 to 21 (@tbl-expcond).

```{r}
#| label: tbl-expcond
#| output: TRUE
#| tbl-cap: "Number of respondents in the control and experimental conditions."

pilot |> freq(stim) |> 
        na.omit() |> 
        kbl(digits = 1)

```

The manipulation check for the question showed that respondents who were exposed to a stimulus that contained a question were significantly more likely to answer "Yes" to `Q24` ("Did the meme you just viewed contain a question?"; @tbl-mcheck). Note that the control condition did not contain a question.

```{r}
#| label: tbl-mcheck
#| output: TRUE
#| tbl-cap: "Manipulation check for presence of a question."

tbl |> 
        kbl()

```

# Situational Curiosity

```{r}
#| label: DVs

source(here::here("scripts", "03_DVs.R"))

```

Cleaned the items `Q25_1` through `Q25_4` and determined the Cronbach's alpha ($\alpha = .95$). Did not run a factor analysis since the correlation matrix showed high significant ($p < .001$) inter-item correlations ranging from $0.74$ to $0.89$. Combined items in a mean index ($M = 3.65$, $SD = 1.65$).

There were no significant differences in the mean of situational curiosity across conditions (@fig-means).

```{r}
#| label: fig-means
#| output: TRUE
#| fig-cap: "Mean of situational curiosity by experimental condition."

pilot |> 
        select(curious, stim) |> 
        na.omit() |> 
        ggplot(aes(x = stim, y = curious)) +
        scale_y_continuous(name = "Situational curiosity",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

Examined the cleaned versions of the individual items (`Q25_1c` thru `Q25_4c`).

```{r}
#| label: fig-means1
#| output: TRUE
#| fig-cap: "Mean of Q25_1c by experimental condition."

pilot |> 
        select(Q25_1c, stim) |> 
        na.omit() |> 
        ggplot(aes(x = stim, y = Q25_1c)) +
        scale_y_continuous(name = "... made you curious.",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-means2
#| output: TRUE
#| fig-cap: "Mean of Q25_2c by experimental condition."

pilot |> 
        select(Q25_2c, stim) |> 
        na.omit() |> 
        ggplot(aes(x = stim, y = Q25_2c)) +
        scale_y_continuous(name = "... captured your interest.",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-means3
#| output: TRUE
#| fig-cap: "Mean of Q25_3c by experimental condition."

pilot |> 
        select(Q25_3c, stim) |> 
        na.omit() |> 
        ggplot(aes(x = stim, y = Q25_3c)) +
        scale_y_continuous(name = "... captured your attention.",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-means4
#| output: TRUE
#| fig-cap: "Mean of Q25_4c by experimental condition."

pilot |> 
        select(Q25_4c, stim) |> 
        na.omit() |> 
        ggplot(aes(x = stim, y = Q25_4c)) +
        scale_y_continuous(name = "... made you want to know more.",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```