---
title: "Curiosity Project: Qualtrics Data Analysis (April 2026)"
format: 
  html:
        toc: true
        number-sections: true
  pdf:
        toc: true
        number-sections: true
        keep-tex: true
        include-in-header:
                text: |
                  \usepackage{fvextra}
                  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
        include-before-body: 
                text: |
                  \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
                  showspaces = false,
                  showtabs = false,
                  breaksymbolleft={},
                  breaklines
                  }
execute: 
  echo: false
  output: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup

source(here::here("scripts", "01_setup.R"))

```

Data for this project were collected between May 5-10, 2026, via Qualtrics. The raw data file contained $1,002$ responses. Of these, $1,000$ respondents who live in the US consented to participate.

```{r}
#| label: tbl-descriptives
#| output: TRUE
#| tbl-cap: Demographics of the sample.

cdata |> 
    select(age, female, educ, Hispanic, Black, White) |> 
    na.omit() |> 
    gtsummary::tbl_summary(
        statistic = list(all_continuous() ~ "{mean} ({sd})", 
        all_categorical() ~ "{n} ({p}%)"
    ))

```

# Experimental Conditions
The experiment embedded in the online survey has a 2 (curiosity prime: absent/present) $\times$ 2 (inclusion of resolution: absent/present) between-subjects design (@tbl-exp-cond). Respondents were randomly assigned to experimental conditions.

```{r}
#| label: exp-cond

source(here::here("scripts", "02_exp-cond.R"))

```

```{r}
#| label: tbl-exp-cond
#| output: TRUE
#| tbl-cap: Experimental conditions.

cdata |> 
  select(stim, cstim, rstim) |> 
  gtsummary::tbl_summary(
    label = list(
      stim = "All experimental conditions",
      cstim = "Curiosity conditions",
      rstim = "Resolution conditions"
    ))

```

# Dependent Variable Sets
We also split the sample randomly into separate variables. 

```{r}
#| output: TRUE

cdata |> 
 count(stim, DVset) |> 
  pivot_wider(names_from = stim, values_from = n) |> 
  kbl()

```

# Data Analysis for Special Issue of the ANNALS of the AAPSS
```{r}
#| label: OLS-models-1

source(here::here("scripts", "03_DVs.R"))
source(here::here("scripts", "04_OLS-models.R"))

```
