---
title: "Curiosity Project: Student Pilot Data Analysis (22-Oct-25)"
format: 
  html:
        toc: true
        number-sections: true
  pdf:
        toc: true
        number-sections: true
        keep-tex: true
        include-in-header:
                text: |
                  \usepackage{fvextra}
                  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
        include-before-body: 
                text: |
                  \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
                  showspaces = false,
                  showtabs = false,
                  breaksymbolleft={},
                  breaklines
                  }
execute: 
  echo: false
  output: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup

source(here::here("scripts", "01_setup.R"))

```

The raw data from the student pilot test contained 267 responses. After removing those who did not consent to participate, Aidan's test responses, and respondents who do not reside in the U.S., the final sample size is 263 respondents.

```{r}
#| label: exp-cond

source(here::here("scripts", "02_exp-cond.R"))

```

The random assignment to conditions appears to have worked fine. The number of respondents per condition ranged from 56 to 63 (@tbl-aexpcond and @tbl-rexpcond).

```{r}
#| label: tbl-aexpcond
#| output: TRUE
#| tbl-cap: "Number of respondents in the control and experimental conditions for the astronomy issue."

pilot |> freq(astim) |> 
        na.omit() |> 
        kbl(digits = 1)

```

```{r}
#| label: tbl-rexpcond
#| output: TRUE
#| tbl-cap: "Number of respondents in the control and experimental conditions for the rain/geosmin issue."

pilot |> freq(rstim) |> 
        na.omit() |> 
        kbl(digits = 1)

```

```{r}
#| label: DVs

source(here::here("scripts", "03_DVs.R"))

```

Cleaned the items `Q25_1` through `Q25_4` (astronomy) and `Q46_1` through `Q46_4` (rain/geosmin) and determined the Cronbach's alpha (astronomy: Cronbach's $\alpha = .92$; rain/geosmin: Cronbach's $\alpha = .93$). Combined items in two mean indices.

```{r}
#| label: fig-asitcur
#| output: TRUE
#| fig-cap: "Mean of situational curiosity by experimental condition for the astronomy issue."

pilot |> 
        select(asitcur, astim) |> 
        na.omit() |> 
        ggplot(aes(x = astim, y = asitcur)) +
        scale_y_continuous(name = "Situational curiosity",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-rsitcur
#| output: TRUE
#| fig-cap: "Mean of situational curiosity by experimental condition for the rain/geosmin issue."

pilot |> 
        select(rsitcur, rstim) |> 
        na.omit() |> 
        ggplot(aes(x = rstim, y = rsitcur)) +
        scale_y_continuous(name = "Situational curiosity",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-ainfoseek
#| output: TRUE
#| fig-cap: "Mean of information seeking by experimental condition for the astronomy issue."

pilot |> 
        select(ainfoseek, astim) |> 
        na.omit() |> 
        ggplot(aes(x = astim, y = ainfoseek)) +
        scale_y_continuous(name = "Likelihood of seeking information",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-rinfoseek
#| output: TRUE
#| fig-cap: "Mean of information seeking by experimental condition for the rain/geosmin issue."

pilot |> 
        select(rinfoseek, rstim) |> 
        na.omit() |> 
        ggplot(aes(x = rstim, y = rinfoseek)) +
        scale_y_continuous(name = "Likelihood of seeking information",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-aclosure
#| output: TRUE
#| fig-cap: "Mean of index tapping the extent to which the information provided closure by experimental condition for the astronomy issue."

pilot |> 
        select(aclosure, astim) |> 
        na.omit() |> 
        ggplot(aes(x = astim, y = aclosure)) +
        scale_y_continuous(name = "Extent to which the information provided closure",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
#| label: fig-rclosure
#| output: TRUE
#| fig-cap: "Mean of index tapping the extent to which the information provided closure by experimental condition for the rain/geosmin issue."

pilot |> 
        select(rclosure, rstim) |> 
        na.omit() |> 
        ggplot(aes(x = rstim, y = rclosure)) +
        scale_y_continuous(name = "Extent to which the information provided closure",
                           limits = c(1,7),
                           breaks = seq(1, 7, 1), 
                           expand = c(0,0)) + 
        scale_x_discrete(name = "") +
        theme_apa() +
        stat_summary(fun = mean, geom = "point") +
        stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
        theme(title = element_text(size = 12, face = "bold"),
              axis.title.x = element_text(size = 12, face = "plain"),
              axis.title.y = element_text(size = 12, face = "plain"),
              axis.text = element_text(size = 12, face = "plain"),
              axis.text.x = element_text(angle = 45, hjust = 1))

```


```{r}
#| label: tbl-asitcur
#| output: TRUE
#| tbl-cap: "OLS regression predicting situational curiosity for the astronomy conditions."

pilot |> 
        select(acurious, ainfoseek, aclosure, asitcur, areso, astim) |> 
        na.omit() |> 
        lm(formula = asitcur ~ acurious + areso) |> 
        summ()

```

```{r}
#| label: tbl-rsitcur
#| output: TRUE
#| tbl-cap: "OLS regression predicting situational curiosity for the rain/geosmin conditions."

pilot |> 
        select(rcurious, rinfoseek, rclosure, rsitcur, rreso, rstim) |> 
        na.omit() |> 
        lm(formula = rsitcur ~ rcurious + rreso) |> 
        summ()

```

```{r}
#| label: tbl-ainfoseek
#| output: TRUE
#| tbl-cap: "OLS regression predicting likelihood of seeking information for the astronomy conditions."

pilot |> 
        select(acurious, ainfoseek, aclosure, asitcur, areso, astim) |> 
        na.omit() |> 
        lm(formula = ainfoseek ~ acurious + areso) |> 
        summ()

```

```{r}
#| label: tbl-rinfoseek
#| output: TRUE
#| tbl-cap: "OLS regression predicting likelihood of seeking information for the rain/geosmin conditions."

pilot |> 
        select(rcurious, rinfoseek, rclosure, rsitcur, rreso, rstim) |> 
        na.omit() |> 
        lm(formula = rinfoseek ~ rcurious + rreso) |> 
        summ()

```

```{r}
#| label: tbl-aclosure
#| output: TRUE
#| tbl-cap: "OLS regression predicting the extent to which the information provided closure for participants in the astronomy conditions."

pilot |> 
        select(acurious, ainfoseek, aclosure, asitcur, areso, astim) |> 
        na.omit() |> 
        lm(formula = aclosure ~ acurious + areso) |> 
        summ()

```

```{r}
#| label: tbl-rclosure
#| output: TRUE
#| tbl-cap: "OLS regression predicting the extent to which the information provided closure for participants in the rain/geosmin conditions."

pilot |> 
        select(rcurious, rinfoseek, rclosure, rsitcur, rreso, rstim) |> 
        na.omit() |> 
        lm(formula = rclosure ~ rcurious + rreso) |> 
        summ()

```