---
title: "Curiosity Project: Qualtrics Data Analysis (April 2026)"
format: 
  html:
        toc: true
        number-sections: true
  pdf:
        toc: true
        number-sections: true
        keep-tex: true
        include-in-header:
                text: |
                  \usepackage{fvextra}
                  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
        include-before-body: 
                text: |
                  \RecustomVerbatimEnvironment{verbatim}{Verbatim}{
                  showspaces = false,
                  showtabs = false,
                  breaksymbolleft={},
                  breaklines
                  }
execute: 
  echo: false
  output: false
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup

source(here::here("scripts", "01_setup.R"))

```

Data for this project were collected between May 5-10, 2026, via Qualtrics. The raw data file contained $1,002$ responses. Of these, $1,000$ respondents who live in the US consented to participate.

```{r}
#| label: tbl-descriptives
#| output: TRUE
#| tbl-cap: Demographics of the sample.

cdata |> 
    select(age, female, educ, Hispanic, Black, White) |> 
    na.omit() |> 
    gtsummary::tbl_summary(
        statistic = list(all_continuous() ~ "{mean} ({sd})", 
        all_categorical() ~ "{n} ({p}%)"
    ))

```

# Experimental Conditions
The experiment embedded in the online survey has a 2 (curiosity prime: absent/present) $\times$ 2 (inclusion of resolution: absent/present) between-subjects design (@tbl-exp-cond). Respondents were randomly assigned to experimental conditions.

```{r}
#| label: exp-cond

source(here::here("scripts", "02_exp-cond.R"))

```

```{r}
#| label: tbl-exp-cond
#| output: TRUE
#| tbl-cap: Experimental conditions.

cdata |> 
  select(stim, cstim, rstim) |> 
  gtsummary::tbl_summary(
    label = list(
      stim = "All experimental conditions",
      cstim = "Curiosity conditions",
      rstim = "Resolution conditions"
    ))

```

# Dependent Variable Sets
We also split the sample randomly into separate variables. 

```{r}
#| output: TRUE

cdata |> 
 count(stim, DVset) |> 
  pivot_wider(names_from = stim, values_from = n) |> 
  kbl()

```

# Data Analysis for Special Issue of the ANNALS of the AAPSS
```{r}
#| label: OLS-models-1

source(here::here("scripts", "03_DVs.R"))
source(here::here("scripts", "04_OLS-models.R"))

```

```{r}
#| label: tbl-OLS-1
#| output: TRUE
#| tbl-cap: Unstandardized regression coefficients (standard errors in parentheses followed by p-values) for regression models in the path analysis predicting intentions to engage in dialogue about astrobiology and space science. 
huxreg(
  "Curiosity" = mcur,
  "Frustation" = mfrus,
  "Dialogue" = mdialogue,
  number_format = 2,
  stars = c(`***` = 0.001, `**` = 0.01, `*` = 0.05),
  ci_level = .95,
  align = ".",
  statistics = c(
    "N" = "nobs",
    "Adj. R-squared" = "adj.r.squared",
    "F" = "statistic",
    "df" = "df",
    "p" = "p.value"
  ),
  error_format = "({std.error})",
  error_pos = c("same"),
  coefs = c(
    "(Intercept)" = "(Intercept)",
    "Curiosity prime (present)" = "cstimCuriosity",
    "Resolution (present)" = "rstimResolution",
    "Frustration" = "frustration",
    "Trait curiosity" = "dispcurious",
    "Situational curiosity" = "curiosity",
    "Resolution (present) × Trait curiosity" = "rstimResolution:dispcurious",
    "Curiosity prime (present) × Resolution prime (present)" = "cstimCuriosity:rstimResolution",
    "Curiosity prime (present) × Resolution prime (present) × Trait curiosity" = "cstimCuriosity:rstimResolution:dispcurious"
  )
)
```

```{r}
#| label: fig-int-1
#| output: TRUE
#| height: 5
#| width: 5
#| fig-cap: Three-way interaction (ns in model) between the curiosity prime and resolution manipulations, and trait curiosity predicting intentions to engage in dialogue about astrobiology.

interact_plot(
        model = mdialogue,
        pred = cstim,
        modx = dispcurious,
        mod2 = rstim,
        mod2.labels = c("No resolution", "Resolution"),
        interval = TRUE,
        int.type = c("confidence"),
        int.width = 0.95,
        legend.main = "Trait curiosity"
) +
        scale_y_continuous(
                name = "Dialogic intentions",
                limits = c(1, 7),
                expand = c(0, 0),
                breaks = seq(1, 7, 1)
        ) +
        scale_x_discrete(
                name = "Curiosity prime",
                labels = c("absent", "present")
        ) +
        jtools::theme_apa(legend.use.title = TRUE)

```
